PANCHANGE_data_preprocessing

### 2020-08-25 PANCHANGE_data_preprocessing2020-07-15.Rmd
re-running pre-processing

```{r Check psychotic_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id %>%
  select(
    autism_spectrum_disorder,
    autism_spectrum_disorder_numeric,
    mhd.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric
  )
}
```

```{r}
mhd.raw.id %>%
  freq(mhd.autism_aspergers_or_autistic_spectrum_disorder)

mhd.raw.id %>%
  freq(mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric)

>>>>

```{r Check psychotic_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id %>%
  select(
    autism_spectrum_disorder,
    autism_spectrum_disorder_numeric,
    mhd.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric
  ) %>%
    filter(autism_spectrum_disorder == "Autism spectrum disorder")
}
```
